### 2020-09-17 README.Rmd
update readme, move contribs list in redame to txt file to avoid cran url check errors

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![cran checks](https://cranchecks.info/badges/worst/taxize)](https://cranchecks.info/pkgs/taxize)
[![R-CMD-check](https://github.com/ropensci/taxize/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/taxize/actions/)
[![codecov](https://codecov.io/gh/ropensci/taxize/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/taxize)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/taxize)](https://github.com/metacran/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/taxize)](https://cran.r-project.org/package=taxize)

@@

* Please [report any issues or bugs](https://github.com/ropensci/taxize/issues).
* License: MIT
* Get citation information for `taxize` in R doing `citation(package = 'taxize')`
* Please note that this project is released with a [Contributor Code of Conduct][coc].
By participating in this project you agree to abide by its terms.

@@

[coc]: https://github.com/ropensci/taxize/blob/master/CODE_OF_CONDUCT.md

>>>>

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![cran checks](https://cranchecks.info/badges/worst/taxize)](https://cranchecks.info/pkgs/taxize)
[![R-CMD-check](https://github.com/ropensci/taxize/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/taxize/actions/)
[![codecov](https://codecov.io/gh/ropensci/taxize/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/taxize)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/taxize)](https://github.com/r-hub/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/taxize)](https://cran.r-project.org/package=taxize)

@@

* Please [report any issues or bugs](https://github.com/ropensci/taxize/issues).
* License: MIT
* Get citation information for `taxize` in R doing `citation(package = 'taxize')`
* Please note that this package is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/). By contributing to this project, you agree to abide by its terms.

@@
